---
title: "Map"
author: "Anna Talucci"
date: "2023-05-26"
output: html_document
---


# Overview

# Packages
```{r}
library(sf)
library(terra)
library(tidyverse)
library(gdalUtilities)
library(topmodel)
library(tidyterra)
library(ggspatial)
library(cowplot)
```

# Projections 

Russia Equal area projection

```{r}
ee_proj = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs "
```

```{r}
laea <- "+proj=laea +lat_0=90 +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs" 
```

# SHP data
```{r}

pts = st_read("../data/points/cn_tr1_ee_pt.shp", 'cn_tr1_ee_pt')
```
# Raster Data

## UAV

```{r}
uav <- rast("../data/raster/CYN_TR1_Fl015.tif")
```

```{r}
uav
```

# Landsat
```{r}
ls <- rast("../data/raster/RGBimageLandsat.tif")
```

```{r}
ls
```

# Sentinel
```{r}
sentinel <- rast("../data/raster/RGBimageSentinel.tif")
```

```{r}
sentinel
```

# Modis
```{r}
modis <- rast("../data/raster/RGBimageModis.tif")
```

```{r}
modis
```

# Reproject
```{r eval=FALSE, include=FALSE}
uav = terra::project(uav, "EPSG:4326")
```

```{r}
ls1 = terra::project(ls, '+proj=aea +lat_0=56 +lon_0=100 +lat_1=50 +lat_2=70 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs')
```

```{r}
modis1 = terra::project(modis, '+proj=aea +lat_0=56 +lon_0=100 +lat_1=50 +lat_2=70 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs')
```

# Basic plots
## UAV
```{r eval=FALSE, include=FALSE}
plotRGB(uav,
        r = 1, g = 2, b = 3)
```

## Landsat
```{r eval=FALSE, include=FALSE}
plotRGB(ls,
        r = 1, g = 2, b = 3, stretch='lin')
```

# Sentinel
```{r eval=FALSE, include=FALSE}
plotRGB(sentinel,
        r = 1, g = 2, b = 3, stretch='lin')
```

# Modis

```{r eval=FALSE, include=FALSE}
plotRGB(modis,
        r = 1, g = 2, b = 3, stretch='lin')
```

# GGPLOT2
## UAV
```{r}
ggplot() +
  geom_spatraster_rgb(data = uav) +
  # You can use coord_sf
  coord_sf(crs = '+proj=aea +lat_0=56 +lon_0=100 +lat_1=50 +lat_2=70 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs',  xlim = c(161.472, 161.478), ylim = c(68.781, 68.785), expand = TRUE)
```


```{r}

(zoom <- data.frame(xmin = 2141201.50, xmax = 2141258.97, ymin = 2497406.67, ymax = 2497450.93)) #Replace numeric values

fieldPts = data.frame(xmin=2141125, ymin=2497340, xmax=2141260, ymax=2497546)
```



```{r}
ggplot() +
  geom_spatraster_rgb(data = uav) +
  # You can use coord_sf
  coord_sf(crs = '+proj=aea +lat_0=56 +lon_0=100 +lat_1=50 +lat_2=70 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs') +
  geom_rect(data = fieldPts, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), alpha = 0, colour = "#000080", size = 1.5, linetype = 1) 
```

```{r}
e <- ext(2141125, 2141260, 2497340, 2497546)
# crop landsat by the extent
uavcrop <- crop(uav, e)
```

```{r}
( uavField = ggplot() +
  geom_spatraster_rgb(data = uavcrop) +
  # You can use coord_sf
   annotation_scale(location = "bl", width_hint = 0.25, text_size = 12, text_face = "bold", text_family = "sans", text_col = "black") +
  coord_sf(crs = '+proj=aea +lat_0=56 +lon_0=100 +lat_1=50 +lat_2=70 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs') + 
   theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))
  
)
```

```{r}
ggsave("../figures/UAVFieldRGB.png", plot = uavField, dpi = 600)
```
### Super zoom
```{r}
ezoom <- ext(2141202, 2141258, 2497406, 2497450)
# crop landsat by the extent
uavzoom <- crop(uav, ezoom)
```

```{r}
( uavzoom = ggplot() +
  geom_spatraster_rgb(data = uavzoom) +
  # You can use coord_sf
   annotation_scale(location = "bl", width_hint = 0.25, text_size = 12, text_face = "bold", text_family = "sans", text_col = "black") +
  coord_sf(crs = '+proj=aea +lat_0=56 +lon_0=100 +lat_1=50 +lat_2=70 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs') +
   theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))
)
```


```{r eval=FALSE, include=FALSE}
ggsave("../figures/UAVZoomRGB.png", plot = uavzoom, dpi = 600)
```

### Zoom2
```{r}
ezoom2 <- ext(2141215, 2141245, 2497420, 2497435)
# crop landsat by the extent
uavzoom2 <- crop(uav, ezoom2)
```
annotation_scale(location = "bl", width_hint = 0.25, text_size = 6, text_face = "plain", text_family = "sans", text_col = "white", pad_x=unit(3,"mm"), pad_y=unit(3,"mm")) +
```{r}
( uavzoom2 = ggplot() +
  geom_spatraster_rgb(data = uavzoom2) +
  # You can use coord_sf
   annotation_scale(location = "bl", width_hint = 0.25, text_size = 6, text_face = "bold", text_family = "sans", text_col = "black", pad_x=unit(4,"mm"), pad_y=unit(3,"mm")) +
  coord_sf(crs = '+proj=aea +lat_0=56 +lon_0=100 +lat_1=50 +lat_2=70 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs') +
   theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) +
    theme_map()
)
```


## landsat
```{r}
ls1
```

(xmin=2141125,  xmax=2141260, ymin=2497340, ymax=2497546)
```{r}
els <- ext(2140142, 2145134, 2495891, 2499251)
# crop landsat by the extent
lscrop <- crop(ls1, els)
```

```{r}
(landsat = ggplot() +
  geom_spatraster_rgb(data = lscrop, max_col_value=70) +
  # You can use coord_sf
   annotation_scale(location = "bl", width_hint = 0.25, text_size = 12, text_face = "bold", text_family = "sans", text_col = "black") +
  coord_sf(crs = '+proj=aea +lat_0=56 +lon_0=100 +lat_1=50 +lat_2=70 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs') +
  geom_rect(data = fieldPts, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), alpha = 0, colour = "red", size = .5, linetype = 1) +
   theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))
)
```


```{r eval=FALSE, include=FALSE}
ggsave("../figures/LandsatRGB.png", plot = landsat, dpi = 600)
```

### Landsat2
```{r}
els2 <- ext(2140242, 2143134, 2495891, 2499251)
# crop landsat by the extent
lscrop2 <- crop(ls1, els2)
```

```{r}
(landsat2 = ggplot() +
  geom_spatraster_rgb(data = lscrop2, max_col_value=70) +
  # You can use coord_sf
   annotation_scale(location = "bl", width_hint = 0.25, text_size = 6, text_face = "plain", text_family = "sans", text_col = "white", pad_x=unit(3,"mm"), pad_y=unit(3,"mm")) +
  coord_sf(crs = '+proj=aea +lat_0=56 +lon_0=100 +lat_1=50 +lat_2=70 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs') +
  geom_rect(data = zoom, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), alpha = 0, colour = "yellow", size = .5, linetype = 1) +
   theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) +
   theme(axis.text.y = element_text(angle=45, size =4), 
         axis.text.x = element_text(size =4)) 

)
```
## Sentinel
```{r}
ggplot() +
  geom_spatraster_rgb(data = sentinel, max_col_value=77) +
  # You can use coord_sf
  coord_sf(crs = 4326)
```

## Modis


```{r}
modis1
```

(xmin=2141125,  xmax=2141260, ymin=2497340, ymax=2497546)
```{r}
emodis <- ext(2140142, 2145134, 2495891, 2499251)
# crop landsat by the extent
modiscrop <- crop(modis1, emodis)
```

```{r}
(modis_plot = ggplot() +
  geom_spatraster_rgb(data = modiscrop, max_col_value=70) +
  # You can use coord_sf
   annotation_scale(location = "bl", width_hint = 0.25, text_size = 12, text_face = "bold", text_family = "sans", text_col = "black") +
  coord_sf(crs = '+proj=aea +lat_0=56 +lon_0=100 +lat_1=50 +lat_2=70 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs') +
  geom_rect(data = fieldPts, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), alpha = 0, colour = "red", size = .5, linetype = 1) +
   theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))
)
```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/ModisRGB.png", plot = modis_plot, dpi = 600)
```

### Modis2
```{r}
emodis2 <- ext(2140242, 2143134, 2495991, 2499351)
# crop landsat by the extent
modiscrop2 <- crop(modis1, emodis2)
```


```{r}
(modis_plot2 = ggplot() +
  geom_spatraster_rgb(data = modiscrop2, max_col_value=70) +
  # You can use coord_sf
   annotation_scale(location = "bl", width_hint = 0.25, text_size = 6, text_face = "plain", text_family = "sans", text_col = "white", pad_x=unit(3,"mm"), pad_y=unit(3,"mm")) +
  coord_sf(crs = '+proj=aea +lat_0=56 +lon_0=100 +lat_1=50 +lat_2=70 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs') +
  geom_rect(data = zoom, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), alpha = 0, colour = "yellow", size = .5, linetype = 1) +
   theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))  +
   theme(axis.text.y = element_text(angle=45, size =4), 
         axis.text.x = element_text(size =4)) 
)
```



# Combine
width = 3, height = 3.
width = 2.2, height = 3.2,
width = 6, height = 3.5
width = 2.2, height = 3.2,
```{r}

( combinePlots = cowplot::plot_grid(uavzoom, uavField, landsat, modis_plot, ncol=2, labels = 'AUTO') )

```

```{r}
ggsave("../figures/ComboPlots.png", plot = combinePlots, dpi = 600)
```


# Combine 2
```{r}

( combinePlots2 = cowplot::plot_grid(landsat2, modis_plot2, ncol=2) )

```

```{r}

( combinePlots3 = cowplot::plot_grid(uavzoom2, ncol=1) )

```

```{r fig.height=5, fig.width=6}
( combinePlots4 = cowplot::plot_grid(combinePlots3, combinePlots2, nrow=1) +
    draw_label("A", x = 0.05, y = .67, fontfamily = "sans", fontface = "bold", color = "black", size = 10) +
   draw_label("B", x = 0.52, y = .67, fontfamily = "sans", fontface = "bold", color = "black", size = 10) +
   draw_label("C", x = .77, y = .67, fontfamily = "sans", fontface = "bold", color = "black", size = 10) ) 
```

```{r}
ggsave("../figures/ComboPlots4.png", plot = combinePlots4, width=6, height = 5, units='in', dpi = 600, bg='white')
```